---
title: "R Notebook"
output: html_notebook
---


# Load libraries

```{r}
# a
```

```{r}
install.packages("xfun")
```


```{r}
library(tidyverse)
library (MASS)
# library(readr)
# library(haven)
```


# Linear Regression

## Linear regression

```{r}
data(Boston)

# head(Boston,1)
```

```{r}
model <- lm(crim ~ rm+age, data = Boston)
summary(model)
```



## Lasso

## Ridge


## Linear Mixed Model (LMM)

Fixed effect = Parameters that are fixed
Random effect = Parameters that 

```{r, message=false, warning=false}

cd4 <- read_table("./dataset/MACS-cd4-vload0_data.txt", 
                   col_names = FALSE)[,c(1:6)] 
names(cd4) <- c("id", "month", "age", "cd4", "cd8", "vload0")
  
cd4 <- cd4 %>% 
  na.omit(vload0)

cd4 <- cd4 %>%
mutate(log_vload0 = log(vload0))

```


```{r}
library(nlme)

model <- lme(fixed = cd4 ~ log_vload0+month+log_vload0*month,
             random = ~ 1 | id, data=cd4,
             correlation=corAR1(form = ~ 1 | id))


summary(model)
```


# Bayesian Model

## MCMC

```{r}

```

## Hierachical Bayes



# Time Series Model

## AR Model

```{r}
plot(cars)
```


## MA Model



## ARIMA Model



## SARIMA Model


## Vector Auto Regressive



## Granger causality (グレンジャー因果)



## Impulse response function (インパルス応答関数)


## State Space Model (状態空間モデル)


## ANOVA










